---
title: 'Assignment week 3: Plotly'
author: "B vStraaten"
date: "March 14, 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages, message = FALSE}
library(plyr)
library(dplyr)
library(plotly)
library(ggplot2)
library(readr)
library(tidyr)
```

## Data
The Energy Statistics Database contains comprehensive energy statistics on the production, trade, conversion and final consumption of primary and secondary; conventional and non-conventional; and new and renewable sources of energy.

### Acknowledgements
This dataset was kindly published by the United Nations Statistics Division on the UNData site and downloaded from Kaggle.

Source: "https://www.kaggle.com/unitednations/international-energy-statistics/downloads/international-energy-statistics.zip/2"


```{r data, message = FALSE}

# Needs Kaggle acount

data <- read_csv("C:/Users/602773/Downloads/international-energy-statistics.zip")
```

## Clean and Filter the data
This analysis focusses on the developement of the energy mix Germany. Before running the analysis I had to clean and filter the data. See the code below.

```{r europe, echo = TRUE}
# selecting Germany and former German states
data$country_or_area <- revalue(data$country_or_area,
                                 c("German Dem. R. (former)" = "Germany",
                                   "Germany, Fed. R. (former)" = "Germany"))

data <- filter(data, country_or_area == "Germany") 

# renaming commodity transactions
data$commodity_transaction <- recode(data$commodity_transaction,
       'Electricity - total net installed capacity of electric power plants, hydro' = "hydro",
        'Electricity - total net installed capacity of electric power plants, solar' = "solar",
        'Electricity - total net installed capacity of electric power plants, geothermal' = "geothermal",
        'Electricity - total net installed capacity of electric power plants, tide, wave, marine' = "tide_wave_marine",
        'Electricity - total net installed capacity of electric power plants, wind' = "wind",
        'Electricity - total net installed capacity of electric power plants, nuclear' = "nuclear",
       'Electricity - total net installed capacity of electric power plants, combustible fuels' = "combustible_fuels")

# selecting commodity transactions
scope <- c("hydro", "geothermal", "solar", "tide_wave_marine", "wind", "nuclear", "combustible_fuels")

data <- filter(data, commodity_transaction %in% scope)

```

## Development of the energy mix in Germany

Click on the energy components in the legend to see their individual development, or select multiple components to make comparisons.

```{r plot, message = FALSE, warning = FALSE, out.width = '100%'}
p1 <- plot_ly(data,
              x = ~year,
              y = ~quantity,
              type = 'bar',
              color = ~commodity_transaction)  %>%
        layout(yaxis = list(title = 'Energy Mix (Kilowatts, thousand)'), barmode = 'stack')
p1
```
